Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology

### 2019-04-18 MainText.Rmd
results added as of now

# Methods

@@

<!--Q3 : metapopulation results : switching near rc for d=0, Fig. 3-->
To examine (Q3), we evaluated extinction risk for each metapopulation model for a wide

>>>>

# Methods \label{methods}

@@

<!--Q3 : metapopulation results : switching near rc for d=0, Fig. 3-->
Following Figs. (\ref{SM-fig_ricker_risk_local_disp_scl_1} - 
\ref{SM-fig_risk_global_disp_abrewer_r_vary_scl_0.6}) we hypothesized the switching 
between the extinction risk generated by left-tail dependent and right-tail dependent noise 
occurred near the critical parameter $r_c$ (see Q3). For simplicity we only consider 
$d=0$ case, i.e., when there was no dispersal between patches (see \nameref{methods}). 
Fig. \ref{fig_extrisk_d0} shows higher extinction risk with left-tail dependent noise 
for $r<r_c$ and with right-tail dependent noise for $r>r_c$. $r_c$ was the vertical
line in Fig. \ref{fig_extrisk_d0} indicating the value of $r$ for each model where 
their deterministic analog switches from under- to over-compensatory dynamics. 
Though the switching visually appered far from the theoretical $r_c$ value for Verhulst 
and Austin-Brewer model, they were consistent with our hypothesis as they had comperatively 
smaller range of $r$ than the other models.
